### 2022-05-27 chapters/04-chapter-4.tex
txs auto checkin

%		\begin{longtable}[l]{  @{}| p{0.7cm} | p{5cm} | p{2cm} | p{2cm} | p{4cm} | @{} }
%			\caption{Kasus-kasus pengujian}
%			\label{testcase-i}                                                           
%			\\ \hline
%			\centering\bfseries{ID} & \centering\bfseries{Service (Fungsi)} & \centering\bfseries{Extra Latency} & \centering\bfseries{User} & \centering\bfseries{Keterangan} \tabularnewline \hline
%			\endfirsthead
%			I1 & CheckoutService (placeorder) &  \centering{100ms} & \centering{25} & Kasus extra latency \#1 \\ \hline
%				
%		\end{longtable}
\begin{table}[]
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		\multicolumn{1}{|c|}{ID} & \multicolumn{1}{c|}{Service (Fungsi)} & Extra Latency & User & Keterangan              \\ \hline
		I1                       & CheckoutService (placeorder)          & 100ms         & 25   & Kasus extra latency \#1 \\ \hline
	\end{tabular}
\end{table}

>>>>

%		\begin{longtable}[l]{  @{}| p{0.7cm} | p{5cm} | p{2cm} | p{2cm} | p{4cm} | @{} }
%			\caption{Kasus-kasus pengujian}
%			\label{testcase-i}                                                           
%			\\ \hline
%			\centering\bfseries{ID} & \centering\bfseries{Service (Fungsi)} & \centering\bfseries{Extra Latency} & \centering\bfseries{User} & \centering\bfseries{Keterangan} \tabularnewline \hline
%			\endfirsthead
%			I1 & CheckoutService (placeorder) &  \centering{100ms} & \centering{25} & Kasus extra latency \#1 \\ \hline
%				
%		\end{longtable}
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\multicolumn{1}{|c|}{ID} &
		\multicolumn{1}{c|}{Service (Fungsi)} &
		\multicolumn{1}{l|}{Extra Latency} &
		\multicolumn{1}{l|}{User} &
		Keterangan \\ \hline
		I1 & CheckoutService (placeorder)                                                           & 100ms & 25  & Kasus extra latency \#1                         \\ \hline
		I2 & CheckoutService (placeorder)                                                           & 250ms & 25  & Kasus extra latency \#2                         \\ \hline
		I3 & CheckoutService (placeorder)                                                           & 350ms & 25  & Kasus extra latency \#3                         \\ \hline
		I4 & CheckoutService (placeorder)                                                           & 250ms & 75  & Kasus extra latency dengan peningkatan user \#1 \\ \hline
		I5 & CheckoutService (placeorder)                                                           & 250ms & 150 & Kasus extra latency dengan peningkatan user \#1 \\ \hline
		I6 & CheckoutService (placeorder)                                                           & -     & 25  & Kasus peningkatan kerja CPU                     \\ \hline
		\multirow{4}{*}{I7} &
		CheckoutService (placeorder) &
		\multirow{4}{*}{250ms} &
		\multirow{4}{*}{25} &
		\multirow{4}{*}{Kasus extra latency dengan beberapa service} \\ \cline{2-2}
		& \begin{tabular}[c]{@{}l@{}}ProductCatalog (getproduct\\ listproducts)\end{tabular}     &       &     &                                                 \\ \cline{2-2}
		& ShippingService (getquote)                                                             &       &     &                                                 \\ \cline{2-2}
		& \begin{tabular}[c]{@{}l@{}}RecommendationService \\ (listrecommendations)\end{tabular} &       &     &                                                 \\ \hline
	\end{tabular}
\end{table}
